No Title

### 2017-10-26 paper/paper.tex
satellite sample

Although Illustris-1 has stellar particles, we do not use their
properties to select the satelite population because the smallest
galaxies are barely resolved in stellar mass at magnitudes of
$M_V=9$. We prefer using the dark matter information as the smallest
sub-halos are sampled with $100$ particles. 
For this reason we select the satellite galaxy samples from the

@@

\section{Satellite Spatial Distribution}
\label{sec:SpatialMeasurements}

We base all our results on the description provided by the inertia
tensor defined by the satellites's positions.

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the central galaxy $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We use $\bf{r}_0$ as the position of the central galaxy, and not the
satellites' geometrical center, to allow for a fair comparison once
the angular positions of the satellites are randomized around this
point.

@@

\subsection{Satellite samples}

We compare the satellite distributions in the MW and M31 at fixed
satellite number.
This means that the magnitude cut corresponding to the faintest
satellite included in the sample is different in each case.
We make this choice for two reasons. 
First to always be sure that there is a non-zero number of satellites to make the computations. 
Second, to be able to compare the two halos at a fixed number of
satellites.

We test the shape and alignment statistics for 11 up 15 satellites.
The lowest number corresponds to the number of classical Milky Way
satellites.
The upper limit corresponds to the minimum number of satellites that
can be resolved in the simulations for both halos in each pair. 
In the case of simulations we rank the subhalos by their maximum
circular velocity. 
We do not use their stellar properties because this represents the
lower resolution limit for the hydrodynamics; most of these subhalos
only have one stellar particle belonging to them. 
In contrast, the detected sub-halos have at least 35 dark matter
particles to determine their properties.

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$M_V$ or $V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $5$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

>>>>

Although Illustris-1 has stellar particles, we do not use their
properties to select the satelite population because the smallest
galaxies are barely resolved in stellar mass at magnitudes of
$M_V=9$. We prefer using the dark matter information as the smallest
sub-halos are sampled with at least $35$ particles. 
For this reason we select the satellite galaxy samples from the

@@

\section{Building, Characterizing and Comparing Satellites Spatial Distributions}
\label{sec:SpatialMeasurements}

\subsection{Building Satellite Samples}

We compare the joint satellite distributions in the MW and M31 at fixed
satellite number, $N_s$.
This means that the magnitude cut corresponding to the faintest
satellite included in the sample is different in each case.
We make this choice for two reasons. 
First, to be sure that there is a non-zero number of satellites in the
simulations to make the computations.  
Second, to rule out the influence of satellite numbers in the
statistics.

We compute the satellite statistics fo 11 up to 15 satellites.
The lowest bound corresponds to the number of classical Milky Way
satellites.
The upper limit corresponds to the maximum number of satellites that
can be resolved in both halos for most of the isolated pairs in Illustris-1.
In simulations we rank the subhalos by their maximum
circular velocity, in observations we rank the satellites by its $M_V$
magnitude.

We also use two kinds of satellite distributions. 
The first keeps the positions for the satellites fixed as provided in
the observations/simulations; the second randomizes the angular positions of
the satellites around the central galaxy while keeping its radial
distance fixed. The randomization process is done 100 times for each
galaxy.

\subsection{Describing Samples with the Inertia Tensor}
We base all our results on the description provided by the inertia
tensor defined by the satellites's positions.

\begin{equation}
{\bf{\bar{I}}} = \sum_{k=1}^{N_s}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the central galaxy $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We use $\bf{r}_0$ as the position of the central galaxy, and not the
satellites' geometrical center, to allow for a fair comparison once
the angular positions of the satellites are randomized around this
point.

@@

\subsection{Comparing Satellite Samples}

\subsection{Describing joint satellite distributions}
